Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-01 manuscripts/paper-1/main.tex
Section 1-2 Finished. 3-4-5 Remaining

%%\documentclass[9pt,conference]{IEEEtran}
\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{cite}

@@

    \subsection{Future approach in the FELICE project}
    \label{section:framework_1}
    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation. As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins. Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments. 
    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.

    \section{Conclusion}~\label{section:conclusion}
    The success of the digital twin system depends on its quality, which requires careful evaluation based on several crucial quality attributes. The correctness of the system is measured by how accurately it behaves compared to the real system.
    Completeness assesses whether the digital twin's subsystems and relations match those of the real system. 
    Fidelity refers to the degree of exactness with which the real system is copied and represented.
    Efficiency measures the productivity of the system and the minimum waste during the process. 
    Evolvability is the system's ability to enhance its suitability to its environment through alterations to both its internal and functional structure. 
    Evaluating these quality attributes of the FELICE digital twin system will help ensure its success in effectively integrating human and robot abilities in a collaborative setting, leading to enhanced efficiency and safety in various human-robot collaborative tasks.
    \section*{Acknowledgements}
    TODO

>>>>

\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{cite}

@@

    \label{section:framework_1}
    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation. As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins. Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments. 
    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.

    The success of the digital twin system depends on its quality, which requires careful evaluation based on several crucial quality attributes. The correctness of the system is measured by how accurately it behaves compared to the real system.
    Completeness assesses whether the digital twin's subsystems and relations match those of the real system. 
    Fidelity refers to the degree of exactness with which the real system is copied and represented.
    Efficiency measures the productivity of the system and the minimum waste during the process. 
    Evolvability is the system's ability to enhance its suitability to its environment through alterations to both its internal and functional structure. 
    Evaluating these quality attributes of the FELICE digital twin system will help ensure its success in effectively integrating human and robot abilities in a collaborative setting, leading to enhanced efficiency and safety in various human-robot collaborative tasks.
    \section*{Acknowledgements}
    TODO
